Manuscript

### 2025-03-14 Manuscript_MD_ScoreReLiability.qmd
update results in manuscript

tab_hetES <- read.csv(here("Tables/Heterogeneity_ES.csv"))
tab_hetrel <- read.csv(here("Tables/Results_RMA_alpha.csv"))

@@

knitr::kable(tab_both)
```

Cases incompatible with claims made in W&D and H&S are highlighted using
boldface.

However, what @fig-forest and @tbl-meanES can not inform us about is in
how far the heterogeneity has changed after correcting for
(un)reliability. In @tbl-tauES, the estimates and tests of heterogeneity
concerning uncorrected and corrected ES on the 12 remaining phenomena,
which passed all criteria (1) – (3), can be found. In the table, the
estimate of heterogeneity $\tau$, with the accompanying QE-test
statistic, degrees of freedom and its p-value are reported, separately
for uncorrected and corrected ES.

Most importantly, @tbl-tauES demonstrates that of 12 phenomena assessed,
for seven phenomena we find patterns incompatible with claims made in
W&D and H&S. For those seven phenomena, the reliability attenuation
correction led to an increase in absolute ES heterogeneity $\tau$. For
the remaining five phenomena, estimates of ES heterogeneity were zero
before and after the correction procedure, leading to no change at all.
This leaves three phenomena where the attenuation correction did indeed
lead to a reduction of heterogeneity. However, it is crucial to note
that the hypothesis tests identified statistically significant
heterogeneity in only four out of 12 phenomena and for none of those a
reduction in heterogeneity took place. In all four cases of
statistically significant heterogeneity, the attenuation correction
procedure led to an increase in heterogeneity, contrary to the W&D and
H&S predictions.

To make sure that actual differences in score reliability exist,
heterogeneity in score reliability is assessed, making use of
Reliability Generalization Meta-Analysis (reference). @tbl-RGMA
summarises the results across all 12 phenomena. Overall, scales for
almost all phenomena appear have produced scores with an average score
reliability larger than .7. Only two phenomena (Albarracin_Priming_SAT
and Alter_Analytic_Processing) come with lower score reliability.
However, for those phenomena we could not identify statistically
significant heterogeneity in effect sizes in @tbl-meanES in the first
place. From the phenomena where the ES heterogeneity grew larger as a
result from the attenuation correction procedure, for six out of seven
phenomena, we observe statistically significant heterogeneity in score
reliability. Only the Shnabel_Willingness_Reconcile_Rev project produced
scores where no heterogeneity in score reliability was identified.
However, for this project, it is crucial to note that only a small
number of replications (8), was available for analysis. Since the power
of Cochran’s Q-test for heterogeneity largely depends on the number of
replications, this result is inconclusive.

Despite this one inconclusive result, for the majority of phenomena
where ES heterogeneity is larger after applying an attenuation
correction, a lack of differences in score reliability can not be made
responsible for results contrary to claims made in W&D and H&S. All
seven phenomena came with an average score reliability from .74 to .9
and for six out of seven phenomena we identified statistically
significant heterogeneity in score reliability.

```{r, echo = FALSE}
#| label: tbl-RGMA
#| tbl-cap: Reliability Generalization Meta-Analysis
knitr::kable(x = read.csv(here("Tables/Results_RMA_alpha.csv")))
```

>>>>

tab_hetES <- read.csv(here("Tables/Heterogeneity_ES.csv"))
tab_hetrel <- read.csv(here("Tables/Results_RMA_alpha.csv"))
tab_muES <- read.csv(here("Tables/Mean_ES.csv"))

@@

knitr::kable(tab_both,
             col.names = c("MASC", 
                           "$\\hat{\\mu}_{\\alpha}$ (95%-CI)", 
                           "$\\hat{\\tau}_{\\alpha}$", 
                           "QE (df)", "p", 
                           "$\\hat{\\tau}_{\\delta_0}$", 
                           "QE (df)", "p",
                           "$\\hat{\\tau}_{\\delta}$", 
                           "QE (df)", "p"),
             escape = FALSE)
# 
# tab_one <- data.frame(tab_muES,
#                       tab_hetrel[,c("mu_alpha_str", "tau_alpha", "QE_str", "QEp")])
```

@tbl-tauES contains the results from performing an RG-MA on the
Cronbach's Alpha coefficients of the scales used to measure the 12
remaining phenomena. Additionally, it contains estimates of
heterogeneity for both uncorrected ES ($\delta_0$) and corrected ES
($\delta$), which are central to assess the research questions posed in
section XXX. Most importantly, @tbl-tauES demonstrates that for all but
one of the phenomena, the attenuation correction procedure barely has an
impact on the extent of ES heterogeneity. For all phenomena but
Srull_Behaviour_Hostility, the heterogeneity in ES before and after the
correction changes very little. This implies that for 11 out of 12
phenomena, differences in score reliability can not be made responsible
for heterogeneity in standardized effect sizes. Only for the
Srull_Behaviour_Hostility phenomenon, accounting for score reliability
actually does reduce, and therefore explain, ES heterogeneity.

Secondly, in @tbl-tauES we find that for ten out of twelve phenomena, ES
heterogeneity grows as a result from the attenuation correction
procedure. Even though these differences tend to be small, it is clear
that in all those cases, not only did accounting for score reliability
not explain any ES heterogeneity, we find even more than initially
expected. This is incompatible with claims made in W&D and H&S, the
attenuation correction increased ES heterogeneity. Concerning the
remaining two phenomena, for the Shnabel_Willingness_Reconcile_Rev, the
reduction in heterogeneity is miniscule and the estimate of
heterogeneity is not statistically significant in the first place. Most
likely, the difference in ES heterogeneity estimates can be explained by
issues of estimation, as only eight replications are available. Again,
only for the Srull_Behaviour_Hostility phenomenon, we find a substantial
reduction in heterogeneity due to the attenuation correction procedure.
However, for the majority of phenomena it appears that differences in
score reliability do not inflate heterogeneity in uncorrected effect
sizes, but instead masks heterogeneity, that can be unveiled by
accounting for score reliability.
